What Does Reproducible Research Mean for Plant Pathology

### 2017-04-05 README.rmd
Update README.rmd and output .md file
Update README.rmd

---
title: "What Does Reproducible Research Mean for Plant Pathology"
author: "A. H. Sparks, E. M. Del Ponte, N. J. Grünwald, and Z. Foster"
output: github_document
---

@@

1.  Adam H. Sparks: Centre for Crop Health, University of Southern Queensland, Toowoomba, Qld 4350, Australia
2.  Emerson M. Del Ponte: Universidade Federal de Viçosa, Viçosa, MG, Brasil
3.  Niklaus J. Grünwald: Horticultural Crops Research Laboratory, USDA Agricultural Research Service, Corvallis, OR 97330, USA
4.  Zachary Foster: Horticultural Crops Research Laboratory, USDA Agricultural Research Service, Corvallis, OR 97330, USA

>>>>

---
title: "What Does Reproducible Research Mean for Plant Pathology"
author: "A. H. Sparks, E. M. Del Ponte, N. J. Grünwald, and Z. Foster"
output: github_document
date: "`r Sys.Date()`"
---

@@

AUTHORS and AFFILIATIONS
========
1.  Adam H. Sparks: Centre for Crop Health, University of Southern Queensland, Toowoomba, Qld 4350, Australia
2.  Emerson M. Del Ponte: Universidade Federal de Viçosa, Viçosa, MG, Brasil
3.  Zachary S. L. Foster: Dept. Botany and Plant Pathology, Oregon State University, Corvallis, OR 97330, USA
4.  Niklaus J. Grünwald: Horticultural Crops Research Laboratory, USDA Agricultural Research Service, Corvallis, OR 97330, USA
